\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-05-12 paper-seb-supplementary-material.tex
Revisions for Computer Journal

A important role of documentation is to cover configuration: how to get code to work --- without configuration, code is generally useless. The most basic is a README file, which explains how to get going; more useful approaches to configuration include make files, which are programs that do the configuration automatically.

@@

There is no code/data distinction one can imagine that cannot easily, even accidentally, be circumvented. In other words, a journal's data policies and code policies should be the identical --- and the conventionally stricter data policies should also apply to code. It is baffling that some journals have data policies that are weaker than their data policies; it is certainly indefensible to have no code policies at all.

@@

The main paper was motivated by selected epidemiological papers and their problematic computational models (which are discussed in the paper). Are the issues illustrated by these case studies typical of science more broadly? We undertook, then, some selected studies of papers in different fields, then undertook a randomized, stratified pilot survey covering several leading peer reviewed journals. The point was not to establish the frequency of problems, so much as to sign whether the problematic case study was exceptional or typical.

@@

The pilot study follows the RAP methodology. The data and code for this paper's pilot survey (and all other analysis used in the paper and in this \supplement) are available on GitHub. All raw data is converted into \LaTeX\ so that the analysis can be typeset directly in the paper; this \supplement\ also contains a complete tabular presentation of the data.

@@

The \RAPstar\ approach cannot enforce the truth of such as summary, but it very significantly increases the chances that the summary is correct and up to date. For example, if refactoring leads to an option being deleted, then it will also disappear \emph{with no further work\/} from the table above. Also, since the summary was proof-read at the same time as proof-reading this \supplement, following \RAPstar\ also increases the chances that any errors or functionality omissions or issues in the makefile have been detected and corrected.

@@

\caption{Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt{covid-sim} \cite{ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the \supplement), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper.  At the time of cloning and checking all repositories in \clonewhen, paper \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ still had nothing in its repository except a single file still saying ``...code coming soon...,'' despite \the\pubdelayinmonths\ months having already elapsed since the submitted paper had claimed the code could be accessed in its repository.}
\label{table-repo-summary}\globalTableLabel{supplementaryTableRepoSummary}
\end{table*}

@@

No evidence of verification and validation was seen. There was only one example of very basic Software Engineering methods, namely independent coding, and even then the independent code used for testing was not uploaded to the paper's code repository, so the independent testing is not available for reviewers or readers of the paper. (See \supplement\ for more details.)

@@

A JavaScript program sanity checks the JSON data. The sanity checks found a few errors (e.g., it checks that if there are comments of any sort then there must be some accessible code; it checks the DOI is accessible, etc), which led to a productive double-checking of all the facts of the original papers --- and correcting all the errors. Some papers that had had no code available during the first assessment had uploaded code by the time of the double-checking.\footnote{{Note that double-checking was performed by the same person as the first assessment, though with the benefit of a six month gap to bring a degree of independence}.} A field \texttt{doubleChecked} was added to supplement the original data field \texttt{accessed} to track the process of double-checking the data; the sanity checks then of course checked all \texttt{doubleChecked} fields were completed.

Note that since JSON data is JavaScript code, it was convenient to combine the data, the data sanity checking, and the analysis all in a single file. Hence, running the data generates the core human-readable information used in this paper.

@@

so the named value is then available for the author to use when the paper is typeset.

@@

All the discussion and examples above were generated automatically, and have been checked correct for other correct values than \the\countUsesVersionControlRepository. This approach, too, considerably helps defend against common Human Factors errors. For example, if we set \texttt{\bslash countUsesVersionControlRepository}=\the\countUsesVersionControlRepository\ to be 2348, say, then all of the subsequent sentences that mention it will say something unexpected and so have to be more carefully proof-read, significantly reducing confirmation bias. The approach turns a possibly-hard-to-spot \emph{single\/} error into \emph{multiple\/} errors spread throughout the paper into different contexts, thus increasing the chances of noticing the error.

@@

If any of the numbers used in a paper were safety critical (e.g., lives directly depend on their values) then further checks would have been made to help detect and avoid errors. \LaTeX\ itself makes it very easy to check that numbers fall within reasonable ranges, or to have any other required safety properties. For the present paper, a potential problem is if the paper is mistakenly typeset \emph{before\/} the latest JSON data has been analyzed; in which case, none of the variables, like \texttt{\bslash countUsesVersionControlRepository}, will have been correctly set and their values could be undefined or nonsense (e.g., from a debugging run of \texttt{data.js}). Variables might be checked as follows:

@@

\noindent
\vbox{\noindent Legend:\vskip 1ex
\input generated/legend.tex
}
%\newpage

>>>>

A important role of documentation is to cover configuration: how to get code to work --- without configuration, code is generally useless. The most basic is a \texttt{README} file, which explains how to get going; more useful approaches to configuration include make files, which are programs that do the configuration automatically.

@@

There is no code/data distinction one can imagine that cannot easily, even accidentally, be circumvented. In other words, a journal's data policies and code policies should be the identical --- and the conventionally stricter data policies should also apply to code. It is baffling that some journals have code policies that are weaker than their data policies; it is certainly indefensible to have no code policies at all.

@@

The main paper was motivated by selected epidemiological papers and their problematic computational models (which are discussed in the paper). Although concerning in their own right, especially for informing national public health policies during a pandemic, the wider question is: are the problems illustrated by these case studies typical of science more broadly? We undertook, then, some selected studies of papers in a variety of fields, then undertook a randomized, stratified pilot survey covering several leading peer reviewed journals. The point was not to establish the frequency of problems, so much as to sign whether the problematic case study was exceptional or typical. It is typical.

@@

The pilot study itself follows the RAP methodology. The data and code for this paper's pilot survey (and all other analysis used in the paper and in this \supplement) are available on GitHub. All raw data is converted into \LaTeX\ so that the analysis can be typeset directly in the paper; this \supplement\ also contains a complete tabular presentation of the data.

@@

The \RAPstar\ approach cannot enforce the truth of such as summary, but it (and the opportunity to read and review it easily) very significantly increases the chances that the summary is correct and up to date. For example, if refactoring leads to an option being deleted, then it will also disappear \emph{with no further work\/} from the table above. Also, since the summary was proof-read at the same time as proof-reading this \supplement, following \RAPstar\ also increases the chances that any errors or functionality omissions or issues in the makefile have been detected and corrected. data.js

@@

\caption{Sizes of repositories, with approximate sizes of code (in kLOC) and data for all available GitHub repositories reviewed in the survey, plus \texttt{covid-sim} \cite{ICmodel} for comparison. Sizes are approximate because in all repositories code and data are conceptually interchangeable (an issue explained in the \supplement), so choices were made in the survey to avoid double-counting. Many repositories rely on downloading additional code and data, which is not counted in the table as the additional required material is not in the repository cited in the paper.  At the time of cloning and checking all repositories in \clonewhen, paper \csname cite-PostoperativeOutcomes.RiskNet\endcsname\ still had nothing in its repository except a single file still saying ``\ldots\ code coming soon~\ldots,'' despite \the\pubdelayinmonths\ months having already elapsed since the  paper had claimed the code could be accessed in its repository.}
\label{table-repo-summary}\globalTableLabel{supplementaryTableRepoSummary}
\end{table*}

@@

No evidence of verification and validation was seen. There was only one example of very basic Software Engineering methods, namely independent coding, and even then the independent code used for testing was not uploaded to the paper's code repository, so the independent testing is not available for reviewers or readers of the paper.

@@

A JavaScript program sanity checks the JSON data. The sanity checks found a few errors (e.g., it checks that if there are comments of any sort then there must be some accessible code in order to have any comments; it checks the DOI is accessible, etc), which led to a productive double-checking of all the facts of the original papers --- and correcting all the errors. Some papers that had had no code available during the first assessment subsequently uploaded code by the time of the double-checking.\footnote{{Note that double-checking was performed by the same person as the first assessment, though with the benefit of a long gap to bring a degree of independence}.} A field \texttt{doubleChecked} was added to supplement the original data field \texttt{accessed} to track the process of double-checking the data. Further sanity checks then of course checked all \texttt{doubleChecked} fields were completed. And so on. Note that since the checking was done automatically in code, whenever any data was modified and whenever the paper was typeset, the entire body of checks were easily rerun.

Since JSON data is effectively JavaScript code, it was convenient to combine the data, the data sanity checking, and the analysis all in a single JavaScript file for more convenient maintenance. Hence, running the data generates the core human-readable information used in this paper.

@@

so the named value (here, \texttt{dataVariableCount}) is then available for the author to use any way they wish when the paper is typeset.

@@

All the discussion and examples above were generated automatically, and have been checked correct for other correct values than \the\countUsesVersionControlRepository. This approach, too, considerably helps defend against common Human Factors errors. For example, if we set \texttt{\bslash countUsesVersionControlRepository}=\the\countUsesVersionControlRepository\ to be 2\hskip .3em 348, say, then all of the subsequent sentences that mention it will say something unexpected and so have to be more carefully proof-read, significantly reducing confirmation bias. The approach turns a possibly-hard-to-spot \emph{single\/} error into \emph{multiple\/} errors spread throughout the paper into different contexts, thus increasing the chances of noticing the error.

@@

If any of the numbers used in a paper were safety critical (e.g., lives directly depend on their values) then further checks would have been made to help detect and avoid errors. \LaTeX\ itself makes it very easy to check that numbers fall within reasonable ranges, or to have any other required safety properties. For the present paper, a potential problem is if the paper is mistakenly typeset \emph{before\/} the latest JSON data has been analyzed; in which case, none of the variables, like \texttt{\bslash countUsesVersionControlRepository}, will have been correctly set and their values could be undefined or nonsense (e.g., from a debugging run of \texttt{data.js}). Although the following text only shows the result of checking (and not the calculations), in general all generated variables can be sanity checked in \LaTeX\ or in the generating programs like \texttt{data.js}:

@@

\noindent
\begin{center}
\sf
\input generated/legend.tex
\end{center}
%\newpage
